### 2023-05-14 presentation/slides/aquisicao.tex
Segundo commit

\begin{frame}
	\frametitle{O sistema 10-20 de posicionamento de eletrodos}
	\begin{columns}
		\begin{column}{0.3\textwidth}
			\par De acordo com \cite{ScienceOpenVid:5960cfa8-7fde-441c-8592-35fdb9841499} os eletrodos responsáveis pela captação do sinal devem ser dispostos segundo um espaçamento de 20\% do tamanho da cabeça do paciente respeitando-se uma 'margem' de 10\% em relação ao \textit{nasion}, \textit{inion} e ao ponto pré-auricular.
		\end{column}
		\begin{column}{0.7\textwidth}
			\begin{figure}
				\centering
				\includegraphics[width=\linewidth]{images/sistema10-20}
				\caption{Ilustração do sistema 10-20 fonte: \cite{sistema10-20}}
				\label{fig:sistema10-20}
			\end{figure}
		\end{column}
	\end{columns}
\end{frame}

### 2023-05-14 presentation/slides/baseDeDados.tex
Segundo commit

\begin{frame}
	\frametitle{Base de dados}

	\only<1>{
	\par A principio a base de dados usada será a \textit{Open access database of EEG signals recorded during imagined speech}\cite{10.1117/12.2255697} para testes preliminares e desenvolvimento dos algoritmos de filtragem e analise dos sinais.\newline

	\begin{quote}
		Este banco de dados contém as gravações de EEG durante a pronúncia imaginada de vogais e comandos, bem como EEG e gravações de áudio durante a pronúncia de vogais e comandos. A amostra é composta por 15 voluntários argentinos entre 24 e 28 anos de idade, de ambos os sexos; sendo 7 mulheres e 8 homens. O objetivo do banco de dados é permitir a acessibilidade dos registros de EEG durante a fala imaginada para futuras pesquisas voltadas para o desenvolvimento de dispositivos BCI que permitam a classificação de palavras a partir de sua imaginação. 
		\cite{10.1117/12.2255697}
	\end{quote}
	}
	\only<2>{
	\par A base está estruturada de forma que cada linha corresponda a um sujeito sendo que, em cada linha, os dados se organizam do seguinte modo:
	\begin{columns}
		\begin{column}{0.4\textwidth}
			\par F3, F4, C3, C4, P3, P4 são as identificações de cada eletrodo.
			\begin{itemize}
				\item F3 - 0:4095
				\item F4 - 4096:8191
				\item C3 - 8192:12287
				\item C4 - 12288:16383
				\item P3 - 16384:20479
				\item P4 - 20480:24575
				\item modalidade - 24576:24576
				\item estímulo - 24577:24577
			\end{itemize}

		\end{column}
		\begin{column}{0.6\textwidth}
			\begin{figure}
				\centering
				\includegraphics[width=\linewidth]{images/visu03}
				\caption{Colocação dos sensores: Nota-se que apenas uma parcela do sistema 10-20 de colocação dos sensores foi utilizada. Fonte: \cite{10.1117/12.2255697}}
				\label{fig:visu03}
			\end{figure}

		\end{column}
	\end{columns}
	}
	\only<3>{
		\par A modalidade pode ser: 1 - Imaginada, 2 - Pronunciada.
		\par O valor do estímulo pode se encaixar em uma das categorias por vez:
		\begin{itemize}
			\item Letras:
			1 - A, 2 - E, 3 - I, 4 - O, 5 - U
			\item Comandos:
			6 - Arriba, 7 - Abajo, 8 - Adelante, 9 - Atrás, 10 - Derecha, 11 - Izquierda	
		\end{itemize}

		\par Na pesquisa pretende-se gerar uma base própria em parceria com as instituições de saúde da cidade.	
	}
\end{frame}
\begin{frame}
	\frametitle{Amostra dos dados na base}
	\only<1>{
	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{images/visu04}
		\caption{Primeiras linhas e colunas da base de dados}
		\label{fig:visu04}
	\end{figure}
	}
	\only<2>{
	\begin{figure}
		\centering
		\includegraphics[width=.9\linewidth]{images/visu05}
		\caption{Últimas linhas e colunas da base de dados}
		\label{fig:visu05}
	\end{figure}
	}
\end{frame}
\begin{frame}
	\frametitle{Pré-processamento}
	\par Objetivando facilitar a manipulação dos dados foram criados os agrupamentos mostrados na figura \ref{fig:visu06}.
	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{images/visu06}
		\caption{Dados tratados e agrupados}
		\label{fig:visu06}
	\end{figure}
\end{frame}

### 2023-05-14 presentation/slides/estudosDeCaso.tex
Segundo commit

\begin{frame}
	\frametitle{Visualização usada em \cite{currey2023epviz}}
	\begin{columns}
		\begin{column}{0.7\textwidth}
			\begin{figure}
				\centering
				\includegraphics[width=\linewidth]{images/epviz00}
				\caption{EPviz - Visualização por gráficos de linhas}
				\label{fig:epviz00}
			\end{figure}
		\end{column}
		\begin{column}{0.3\textwidth}
			\par A visualização por linhas é eficiente pois nela fica claro os componentes de alta e baixa frequência. No exemplo ao lado o programa EPViz visualiza os sinais captados por todos os eletrodos fornecendo uma boa visão geral. No entanto falta a visão em detalhe que permitiria uma análise mais exata das curvas mostradas.
		\end{column}
	\end{columns}
\end{frame}
\begin{frame}
	\frametitle{Visualização usada em \cite{9098189}}
	\begin{columns}
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\centering
				\includegraphics[width=\linewidth]{images/visu01}
				\caption{Visualização topológica}
				\label{fig:visu01}
			\end{figure}
		\end{column}
		\begin{column}{0.5\textwidth}
			\par A metodologia mostrada neste trabalho usa mapas topológicos de cores para indicar a energia do sinal em cada sensor, dessa forma é possível ver as regiões do cérebro com atividade mais intensa no tempo do sinal correspondente, também é interessante a marcação dos identificadores de cada sensor, no entanto, a visualização faz uma interpolação dos valores medidos levando a uma interpretação não necessariamente verdadeira de que as intensidades variam segundo gradientes. 
		\end{column}
	\end{columns}
\end{frame}
\begin{frame}
	\frametitle{Visualização usada em \cite{8937083}}
	\begin{columns}
		\begin{column}{0.6	\textwidth}
			\par Aqui novamente o problema do gradiente ocorre, porém é importante notar a simplificação na visualização que mostra o estado da atividade cerebral em quatro diferentes momentos do cérebro.
		\end{column}
		\begin{column}{0.4\textwidth}
			\begin{figure}
				\centering
				\includegraphics[width=\linewidth]{images/visu02}
				\caption{Visualização topológica}
				\label{fig:visu02}
			\end{figure}
		\end{column}
	\end{columns}

\end{frame}

### 2023-05-14 presentation/slides/introducao.tex
Segundo commit

\begin{frame}
	\frametitle{Introdução}
	\par Dados de Eletroencefalograma (EEG) tem, em sua natureza, um grande volume, variadas frequências que o compõe $\alpha$(8-13Hz), $\beta$(14-30Hz), $\theta$(4-7Hz), $\sigma$(0.5-3Hz) \cite{8937083}, um número extremamente alto de fontes emissoras (os neurônios) assim como múltiplas possíveis interferências eletromagnéticas (telefones celulares, motores elétricos, campos magnéticos provindos de fios, etc.) Esse trabalho se propõe, baseado nas mais recentes pesquisas que incluem visualização de EEG, propor formas efetivas de mostrar, detalhar e sintetizar essas informações de forma que as imagens geradas sejam de alguma ajuda na pesquisa.
\end{frame}

### 2023-05-14 presentation/slides/proposta.tex
Segundo commit

\begin{frame}
	\frametitle{Proposta}
	\par Construir uma visualização que, além dos gráficos de linha e energia, remeta ao posicionamento dos eletrodos no sistema 10-20 \textbf{sem} o uso de gradientes e que permita:
	\begin{columns}
		\begin{column}{0.42\textwidth}
			\begin{itemize}
				\item selecionar o sujeito e estímulo (interatividade)
				\item visualizar de forma geral e particular cada um dos sinais captados pelos sensores (interatividade)
				\item exibir a origem do sinal
				\item ampliar as curvas geradas (visualizar detalhes)
				\item mostrar o energia total do sinal no intervalo mostrado
				\item uso de cores com alto contraste (percepção)
			\end{itemize}
		\end{column}
		\begin{column}{0.66\textwidth}
			\only<1>{
				\begin{figure}
					\centering
					\includegraphics[width=\linewidth]{images/g3714}
					\caption{Visão geral}
					\label{fig:g3714}
				\end{figure}
			}
			\only<2>{
				\begin{figure}
					\centering
					\includegraphics[width=\linewidth]{images/g3762}
					\caption{Visão específica}
					\label{fig:g3762}
				\end{figure}
			}
		\end{column}
	\end{columns}
\end{frame}
\begin{frame}[allowframebreaks]
	\frametitle{Discussão da proposta}
	\par Tanto a \textbf{seleção do sujeito e estímulo} quanto o a caixa e checagem fazem parte do \textbf{ciclo de visualização} (loop), dessa forma, ao mudar o tipo de visão e/ou o sujeito analisado se tem uma resposta imediata na visualização (Ciclo de Ação de Norman).\newline

	\par As cores de \textbf{alto contraste} permitem localizar a origem dos dados facilmente evitando um problema comum que é a diferenciação dos dados quando cores muito similares são usadas.\newline

	\par A \textbf{ampliação} permite que cada sinal possa ser visto em \textbf{detalhes}, dessa forma, fica mais fácil visualizar as informações vinculadas aos sinais de baixa e alta frequência proporcionando a identificação de \textbf{objetos segundo sua "silhueta"}.\newline

	\par Vale destacar que os atributos usados na proposta tem uma ordenção \textbf{sequêncial} para a amplitude e frequência dos sinais durante o tempo (gráficos de linha) e ao mesmo tempo é \textbf{categórico} pois a análise das frequências podem dizer muito sobre o sujeito que está sendo analizado.\newline
	\par O atributo de energia (barra vertical lateral ao gráfico de linhas) é \textbf{quantitativo}.\newline

	\par Em se tratando de atributos \textbf{categóricos} vale destacar também a região à direita dos gráficos. Essa seção indica quais regiões do cérebro estão enviando quais sinais, dessa forma, é possível, por exemplo, inferir quais regiões do cérebro estão mais ativas quando da execução de algum pensamento e/ou ação.\newline

	\par Nota-se a \textbf{proximidade} utilizada da barras laterais com seus respectivos gráficos de linha.\newline

	\par Em termos de \textbf{categorias semióticas} \cite{santaella2017semiotica} é possivel destacar:
	\begin{itemize}
		\item primeiridade: Cores que destacam e chamam imediatamente a atenção do usuário ou usuária.
		\item secundidade: O conjunto ação/reação aplicado aos controles e imagens.
		\item terceiridade: A consequente interpretação da imagem apresentada assim como os raciocínios necessários para o entedimento do que é mostrado.
	\end{itemize}

\end{frame}

### 2023-05-16 presentation/slides/proposta.tex
Correções
Impressão

@@
 	\frametitle{Discussão da proposta}
-	\par Tanto a \textbf{seleção do sujeito e estímulo} quanto o a caixa e checagem fazem parte do \textbf{ciclo de visualização} (loop), dessa forma, ao mudar o tipo de visão e/ou o sujeito analisado se tem uma resposta imediata na visualização (Ciclo de Ação de Norman).\newline
+	\par Tanto a \textbf{seleção do sujeito e estímulo} quanto o a caixa e checagem fazem parte do \textbf{ciclo de visualização} (loop), dessa forma, ao mudar o tipo de visão e/ou o sujeito analisado se tem uma resposta imediata na visualização.\newline
 
@@
 		\item secundidade: O conjunto ação/reação aplicado aos controles e imagens.
-		\item terceiridade: A consequente interpretação da imagem apresentada assim como os raciocínios necessários para o entedimento do que é mostrado.
+		\item terceiridade: A consequente interpretação da imagem apresentada assim como os raciocínios necessários para o entendimento do que é mostrado.
 	\end{itemize}

### 2023-07-14 dashboard2/data.py
Reading some real data

@@ -1,56 +1,110 @@
-rom dash import Dash, html, dash_table, dcc, Input, Output
-import pandas as pd
-import plotly.express as px
-import plotly.graph_objs as go
-from plotly.subplots import make_subplots
+import panel as pn
+import numpy as np
+from bs4 import BeautifulSoup
+from IPython.display import SVG
+
+import plotly.subplots as sp
+import plotly.graph_objects as go
 
 from scipy.io import loadmat
-import numpy as np
+import pandas as pd
 
-from ipywidgets import interact, Dropdown, IntSlider
-from PIL import Image
+class Dashdata:
+    def __init__(self):
+        
+        ####################
+        ### Loading data ###
+        ####################
+        
+        sensorsTags = [
+               "FP1","FP2",
+               "F3", "F4", "F7", "F8", "FZ",
+               "A1","A2","T3","T4","C3","C4","CZ",
+               "T5","T6","P3","P4","PZ",
+               "O1","O2"
+               ]
 
-def joinIntoArray(start_col, end_col, newColumn, dataframe):
-    cols_to_join = dataframe.iloc[:, start_col:end_col].columns
-    dataframe[newColumn] = dataframe[cols_to_join].apply(lambda x: np.array(pd.to_numeric(x, errors='coerce')), axis=1)
-    dataframe.drop(cols_to_join, axis=1, inplace=True)
+        sensorsColors = [
+            "#FF3C00",  # Vivid Orange
+            "#FF9700",  # Bright Orange
+            "#FFD300",  # Sunflower Yellow
+            "#FF4D6E",  # Coral Pink
+            "#FF66B2",  # Bubblegum Pink
+            "#FF8AC3",  # Light Pink
+            "#FF00D8",  # Magenta
+            "#6A00FF",  # Vivid Purple
+            "#A050FF",  # Lavender Purple
+            "#FFA6FF",  # Cotton Candy
+            "#00C4FF",  # Sky Blue
+            "#00E6FF",  # Aqua Blue
+            "#00FFD4",  # Mint Green
+            "#1AFFB5",  # Turquoise
+            "#00FF89",  # Neon Green
+            "#00FF00",  # Lime Green
+            "#FFFF33",  # Bright Yellow
+            "#F9FF66",  # Lemon Yellow
+            "#FF9F00",  # Amber
+            "#FF7733",  # Coral Orange
[…]

### 2023-07-14 dashboard2/main.py

@@ -6,61 +6,29 @@ from IPython.display import SVG
 import plotly.subplots as sp
 import plotly.graph_objects as go
 
-sensorsTags = [
-       "FP1","FP2",
-       "F3", "F4", "F7", "F8", "FZ",
-       "A1","A2","T3","T4","C3","C4","CZ",
-       "T5","T6","P3","P4","PZ",
-       "O1","O2"
-       ]
-sensorsColors = [
-    "#FF3C00",  # Vivid Orange
-    "#FF9700",  # Bright Orange
-    "#FFD300",  # Sunflower Yellow
-    "#FF4D6E",  # Coral Pink
-    "#FF66B2",  # Bubblegum Pink
-    "#FF8AC3",  # Light Pink
-    "#FF00D8",  # Magenta
-    "#6A00FF",  # Vivid Purple
-    "#A050FF",  # Lavender Purple
-    "#FFA6FF",  # Cotton Candy
-    "#00C4FF",  # Sky Blue
-    "#00E6FF",  # Aqua Blue
-    "#00FFD4",  # Mint Green
-    "#1AFFB5",  # Turquoise
-    "#00FF89",  # Neon Green
-    "#00FF00",  # Lime Green
-    "#FFFF33",  # Bright Yellow
-    "#F9FF66",  # Lemon Yellow
-    "#FF9F00",  # Amber
-    "#FF7733",  # Coral Orange
-    "#FFAF40"   # Peach
-]
+from data import Dashdata
 
-subjectsNamesAndCodes = {
-    'Sujeito01': '1',
-    'Sujeito02': '2',
-    'Sujeito03': '3'
-}
-
-sensorToColorRelationship = dict(zip(sensorsTags, sensorsColors))
+ddata = Dashdata()
 
 # Create the line plot using Plotly graph objects
-num_lines = 3  # Number of lines to plot
+subject = 1  # Number of lines to plot
 
 # Create the SVG pane
-svg_content = open("brain.svg").read()
-svg_image = pn.pane.SVG(SVG(svg_content), width=600, height=600)
+svg_image = pn.pane.SVG(SVG(ddata.brainSvgImage), width=600, height=600)
 
-def readData(seed, num_lines):
+def readData(subject, dataset):
     lines = []
-    for _ in range(num_lines):
-        x = np.random.rand(seed)
-        y = np.random.rand(seed)
-        lines.append((x, y))
[…]

### 2023-07-14 dashboard2/teste.py

@@ -1,0 +1,63 @@
+rom dash import Dash, html, dash_table, dcc, Input, Output
+import pandas as pd
+import plotly.express as px
+import plotly.graph_objs as go
+from plotly.subplots import make_subplots
+
+from scipy.io import loadmat
+import numpy as np
+
+from ipywidgets import interact, Dropdown, IntSlider
+from PIL import Image
+
+def joinIntoArray(start_col, end_col, newColumn, dataframe):
+    cols_to_join = dataframe.iloc[:, start_col:end_col].columns
+    dataframe[newColumn] = dataframe[cols_to_join].apply(lambda x: np.array(pd.to_numeric(x, errors='coerce')), axis=1)
+    dataframe.drop(cols_to_join, axis=1, inplace=True)
+
+def joinIntoValue(start_col, end_col, newColumn, dataframe):
+    cols_to_join = dataframe.iloc[:, start_col:end_col].columns
+    dataframe[newColumn] = dataframe[cols_to_join].apply(lambda x: pd.to_numeric(x, errors='coerce'), axis=1)
+    dataframe.drop(cols_to_join, axis=1, inplace=True)
+
+def loadData():
+    mat = loadmat(
+    '/home/ensismoebius/Documentos/UNESP/doutorado/databases/Base de Datos Habla Imaginada/S01/S01_EEG.mat',
+    struct_as_record=True, squeeze_me=True, mat_dtype=False
+    )
+
+    df = pd.DataFrame(mat['EEG'])
+
+    joinIntoArray(0, 4096, 'F3', df)
+    joinIntoArray(0, 4096, 'F4', df)
+    joinIntoArray(0, 4096, 'C3', df)
+    joinIntoArray(0, 4096, 'C4', df)
+    joinIntoArray(0, 4096, 'P3', df)
+    joinIntoArray(0, 4096, 'P4', df)
+    
+    joinIntoValue(0, 1, 'Modalidade', df)
+    joinIntoValue(0, 1, 'Estímulo', df)
+    joinIntoValue(0, 1, 'Artefatos', df)
+    
+    return mat
+
+def getEstimulos():
+        estimulos = {
+            1  : "A",
+            2  : "E",
+            3  : "I",
+            4  : "O",
+            5  : "U",
+            6  : "Arriba",
+            7  : "Abajo",
+            8  : "Adelante",
+            9  : "Atrás",
+            10 : "Derecha",
+            11 : "Izquierda",
+        }
+        
[…]

### 2023-07-14 dashboard2/main.py
Trying to create a clas for UI

@@ -8,28 +8,147 @@ import plotly.graph_objects as go
 
 from data import Dashdata
 
-ddata = Dashdata()
+class Dashboard(pn.Row):
+    def __init__(self):
+        # Data container
+        self.ddata = Dashdata()
+        
+        # Create the SVG pane
+        self.svg_image = pn.pane.SVG(
+            SVG(self.ddata.brainSvgImage), 
+            width=600, 
+            height=600)
+        
+        # Create the slider
+        intRangeSliderWidget = pn.widgets.IntSlider(
+            name='Integer Range Slider',
+            start=0, end=10000, value=0, step=1)
+        
+        # Create the Plotly pane
+        plot_pane = pn.pane.Plotly()
+        
+        # Bind the slider value to the update_plot function
+        intRangeSliderWidget.param.watch(update_plot, 'value')
+        
+        selectWidget = pn.widgets.Select(
+            name='Selecione a sujeito',
+            groups=ddata.subjectsNamesAndCodes
+        )
+        
+        selectWidget.param.watch(self._selectData, 'value')
+        
+        switchLabelWidget = pn.widgets.StaticText(name='Visão geral', value='')
+        switchWidget = pn.widgets.Switch(name='Visão geral')
+        
+        self = pn.Row(
+            svg_image, 
+            pn.Column(
+                pn.Row(intRangeSliderWidget, selectWidget),
+                plot_pane,
+                pn.Row(switchLabelWidget, switchWidget)
+                ), 
+            sizing_mode='stretch_width')
 
-# Create the line plot using Plotly graph objects
-subject = 1  # Number of lines to plot
+    def _selectData(event):
+        selected_option = event.obj.value
+        return selected_option
+        
+    def _changeElementHeight(soup, element_id, new_height):
+        element = soup.find(id=element_id)
+        if element is not None:
+            element['height'] = str(new_height/1000)
+
+    def _paintSensor(soup, sensorsTags):
+        element = soup.find(id=sensorsTags)
+        if element is not None:
+            color = ddata.sensorToColorRelationship[sensorsTags]
+            element["style"] = f'fill:{color}'
+            
+    def updateBrainFigure(event, svg_image):
[…]

### 2023-07-14 dashboard2/data.py
Sensor and Svg are in sinc

@@ -1,13 +1,6 @@
-import panel as pn
 import numpy as np
-from bs4 import BeautifulSoup
-from IPython.display import SVG
-
-import plotly.subplots as sp
-import plotly.graph_objects as go
-
-from scipy.io import loadmat
 import pandas as pd
+from scipy.io import loadmat
 
 class Dashdata:
     def __init__(self):

### 2023-07-14 dashboard2/main.py

@@ -1,51 +1,59 @@
 import panel as pn
-import numpy as np
+import plotly.subplots as sp
 from bs4 import BeautifulSoup
 from IPython.display import SVG
-
-import plotly.subplots as sp
 import plotly.graph_objects as go
 
 from data import Dashdata
 
-class Dashboard(pn.Row):
+class Dashboard():
     def __init__(self):
         # Data container
         self.ddata = Dashdata()
         
-        # Create the SVG pane
+        # Create the SVG pane widget
         self.svg_image = pn.pane.SVG(
             SVG(self.ddata.brainSvgImage), 
             width=600, 
             height=600)
         
-        # Create the slider
-        intRangeSliderWidget = pn.widgets.IntSlider(
-            name='Integer Range Slider',
-            start=0, end=10000, value=0, step=1)
+        ########################
+        ### Widgets creation ###
+        ########################
         
-        # Create the Plotly pane
-        plot_pane = pn.pane.Plotly()
+        # Create the Plotly pane widget
+        self.plot_pane = pn.pane.Plotly()
         
-        # Bind the slider value to the update_plot function
-        intRangeSliderWidget.param.watch(update_plot, 'value')
+        # Create the slider widget
+        self.intRangeSliderWidget = pn.widgets.IntSlider(name='Integer Range Slider', start=0, end=10, value=0, step=1)
         
-        selectWidget = pn.widgets.Select(
-            name='Selecione a sujeito',
-            groups=ddata.subjectsNamesAndCodes
-        )
+        # Create the selection widget
+        self.selectWidget = pn.widgets.Select(name='Selecione a sujeito', groups=self.ddata.subjectsNamesAndCodes)
+
+        # Create a label for the switch widget
+        self.switchLabelWidget = pn.widgets.StaticText(name='Visão geral', value='')
         
-        selectWidget.param.watch(self._selectData, 'value')
+        # Create the switch widget
+        self.switchWidget = pn.widgets.Switch(name='Visão geral')
+
+        ############################
+        ### Event handle binding ###
+        ############################
+
+        # Bind the widgets to its respective event handler
+        self.intRangeSliderWidget.param.watch(self._update_plot, 'value')
[…]

### 2023-07-14 dashboard2/main.py
Energy are calculated and non-existent sensor are not shown

@@ -1,4 +1,5 @@
 import panel as pn
+import numpy as np
 import plotly.subplots as sp
 from bs4 import BeautifulSoup
 from IPython.display import SVG
@@ -72,15 +73,29 @@ class Dashboard():
             color = self.ddata.sensorToColorRelationship[sensorsTags]
             element["style"] = f'fill:{color}'
             
-    def updateBrainFigure(self, event, svg_image, lines):
-        soup = BeautifulSoup(svg_image.object.data, "xml")
+    def calculate_total_energy(self, values):
+        squared_values = np.square(values)       # Square each value
+        sum_of_squares = np.sum(squared_values)  # Sum up the squared values
+        total_energy = np.sqrt(sum_of_squares)   # Take the square root
+    
+        return total_energy
+            
+    def updateBrainFigure(self, event, lines):
         
+        # Loads the SVG
+        soup = BeautifulSoup(self.ddata.brainSvgImage, "xml")
+        
+        # Iterates over all available sensors
         for i, line in enumerate(lines):
+            
+            # Change sensor color
             self._paintSensor(soup, line[0])
-            self._changeElementHeight(soup, line[0] +"bar", event)
+            
+            # Change sensor energy height
+            self._changeElementHeight(soup, line[0] +"bar", 10 * self.calculate_total_energy(line[1]))
             
         # Must be the last call!
-        svg_image.object = SVG(str(soup))
+        self.svg_image.object = SVG(str(soup))
         
     def _update_plot(self, event):
         lines = []
@@ -112,7 +127,7 @@ class Dashboard():
         self.plot_pane.object = fig
 
         # Refresh the Svg UI
-        self.updateBrainFigure(event.new, self.svg_image, lines)
+        self.updateBrainFigure(event.new, lines)
         
         return fig
 

### 2023-07-14 dashboard2/main.py
Almost there!

@@ -66,6 +66,7 @@ class Dashboard():
         element = soup.find(id=element_id)
         if element is not None:
             element['height'] = str(new_height/1000)
+            element["style"] = 'fill:#000000'
 
     def _paintSensor(self, soup, sensorsTags):
         element = soup.find(id=sensorsTags)
@@ -92,7 +93,7 @@ class Dashboard():
             self._paintSensor(soup, line[0])
             
             # Change sensor energy height
-            self._changeElementHeight(soup, line[0] +"bar", 10 * self.calculate_total_energy(line[1]))
+            self._changeElementHeight(soup, line[0] +"bar", 5 * self.calculate_total_energy(line[1]))
             
         # Must be the last call!
         self.svg_image.object = SVG(str(soup))

### 2023-07-15 dashboard2/main.py
System is ready!!!

@@ -7,33 +7,63 @@ import plotly.graph_objects as go
 
 from data import Dashdata
 
+
 class Dashboard():
     def __init__(self):
+
+        #######################
+        ### Core properties ###
+        #######################
+
         # Data container
         self.ddata = Dashdata()
-        
+
+        self.selectedModality = -1
+
+        self.selectedArtifact = -1
+
+        self.selectedEstimuli = -1
+
+        self.generalView = False
+
+        self.subjects = self.ddata.dataframe
+
         # Create the SVG pane widget
         self.svg_image = pn.pane.SVG(
-            SVG(self.ddata.brainSvgImage), 
-            width=600, 
+            SVG(self.ddata.brainSvgImage),
+            width=600,
             height=600)
-        
+
         ########################
         ### Widgets creation ###
         ########################
-        
+
         # Create the Plotly pane widget
         self.plot_pane = pn.pane.Plotly()
-        
-        # Create the slider widget
-        self.intRangeSliderWidget = pn.widgets.IntSlider(name='Integer Range Slider', start=0, end=10, value=0, step=1)
-        
-        # Create the selection widget
-        self.selectWidget = pn.widgets.Select(name='Selecione a sujeito', groups=self.ddata.subjectsNamesAndCodes)
+
+        # Create the subject selection widget
+        self.selectSubjectWidget = pn.widgets.Select(
+            name='Selecione a sujeito')
+
+        # Create the modality selection widget
+        self.selectModalityWidget = pn.widgets.Select(
+            name='Selecione a modalidade')
+        self.selectModalityWidget.options = self.ddata.modalities
+
+        # Create the artfact selection widget
+        self.selectArtefactWidget = pn.widgets.Select(
+            name='Selecione o artefato')
+        self.selectArtefactWidget.options = self.ddata.artfacts
+
+        # Create the estimul selection widget
+        self.selectStimuliWidget = pn.widgets.Select(
+            name='Selecione o estímulo')
+        self.selectStimuliWidget.options = self.ddata.estimulos
 
         # Create a label for the switch widget
-        self.switchLabelWidget = pn.widgets.StaticText(name='Visão geral', value='')
-        
+        self.switchLabelWidget = pn.widgets.StaticText(
+            name='Visão geral', value='')
+
         # Create the switch widget
         self.switchWidget = pn.widgets.Switch(name='Visão geral')
 
@@ -41,27 +71,125 @@ class Dashboard():
         ### Event handle binding ###
         ############################
 
[…]

### 2023-07-15 dashboard2/main.py
Minor fix

@@ -43,7 +43,7 @@ class Dashboard():
 
         # Create the subject selection widget
         self.selectSubjectWidget = pn.widgets.Select(
-            name='Selecione a sujeito')
+            name='Selecione o sujeito')
 
         # Create the modality selection widget
         self.selectModalityWidget = pn.widgets.Select(

### 2023-07-15 dashboard2/main.py
Now in dark mode!

@@ -4,6 +4,7 @@ import plotly.subplots as sp
 from bs4 import BeautifulSoup
 from IPython.display import SVG
 import plotly.graph_objects as go
+from panel.template import DarkTheme
 
 from data import Dashdata
 
@@ -80,16 +81,21 @@ class Dashboard():
         #######################
         ### Layout assembly ###
         #######################
-
-        self.layout = pn.Row(
-            self.svg_image,
-            pn.Column(
-                pn.Row(self.selectModalityWidget, self.selectStimuliWidget),
-                pn.Row(self.selectArtefactWidget, self.selectSubjectWidget),
-                self.plot_pane,
-                pn.Row(self.switchLabelWidget, self.switchWidget)
-            ),
-            sizing_mode='stretch_width')
+        
+        self.layout = pn.template.MaterialTemplate(title='Visualização de ECG', theme=DarkTheme)
+        
+        self.layout.main.append(
+            pn.Row(
+                self.svg_image,
+                pn.Column(
+                    pn.Row(self.selectModalityWidget, self.selectStimuliWidget),
+                    pn.Row(self.selectArtefactWidget, self.selectSubjectWidget),
+                    self.plot_pane,
+                    pn.Row(self.switchLabelWidget, self.switchWidget)
+                ),
+                sizing_mode='stretch_width'
+            )
+        )
 
     ############################
     ### Callbacks definition ###
@@ -102,21 +108,21 @@ class Dashboard():
     def _modalitySelected(self, event):
         self.selectedModality = event.new
         if (self.selectedModality != -1) and (self.selectedEstimuli != -1):
-            self.subjects = self.filterSignals(
+            self.subjects = self._filterSignals(
                 self.selectedModality, self.selectedEstimuli, self.selectedArtifact)
             self.selectSubjectWidget.options = self.subjects.index.tolist()
 
     def _estimuliSelected(self, event):
         self.selectedEstimuli = event.new
         if (self.selectedModality != -1) and (self.selectedEstimuli != -1):
-            self.subjects = self.filterSignals(
+            self.subjects = self._filterSignals(
                 self.selectedModality, self.selectedEstimuli, self.selectedArtifact)
             self.selectSubjectWidget.options = self.subjects.index.tolist()
 
     def _artifactSelected(self, event):
         self.selectedArtifact = event.new
         if (self.selectedModality != -1) and (self.selectedArtifact != -1):
[…]

### 2023-07-16 article/article.tex
Beginning the article

\documentclass[format=acmtog]{acmart}

\title{Visualizing EEG signals}

\author{André Furlan}

\affiliation{
	\institution{UNESP - Universidade Estadual Paulista Júlio de Mesquita Filho}
	\city{São José do Rio Preto}
	\state{André Furlan}
	\country{Brazil}
}
\email{ensismoebius@gmail.com}

\begin{document}

	\begin{abstract}
		Electroencephalogram (EEG) data has inherent complexity, including a large volume, diverse frequencies (e.g., alpha, beta, theta, sigma), and numerous emitting sources (neurons). Additionally, potential electromagnetic interferences from external sources pose challenges during EEG analysis. This work aims to propose effective visualization techniques for EEG data, drawing insights from recent research on EEG visualization. The goal is to create informative visualizations that aid in EEG research by showing detailed representations of the data without the use of misleading gradients. The visualization will include interactive features for subject and stimulus selection, providing a comprehensive understanding of EEG signals with high-contrast color schemes to enhance perceptual clarity.
	\end{abstract}

	\maketitle

	\section{Introduction}
		\par Electroencephalogram (EEG) data is widely used in neuroscience research to study brain activity. EEG records electrical signals generated by brain neurons and reflects cognitive processes, making it a valuable tool in various applications, including Brain-Computer Interfaces (BCI) and clinical diagnosis of neurological disorders \cite{8937083}. Analyzing EEG data, however, poses challenges due to its complexity, such as a vast number of emitting sources (neurons) and potential electromagnetic interferences from external sources like cell phones, electric motors, and magnetic fields from wires \cite{8937083}. To facilitate EEG data interpretation and visualization, it is crucial to develop effective and efficient visualization techniques that allow researchers to gain valuable insights from the data. This paper proposes a novel visualization method for EEG data, combining line graphs and energy visualizations with a display of the electrode positions in the 10-20 system \cite{sistema10-20}. The proposed visualization will be interactive, allowing users to select subjects and stimuli and explore specific signal details. The goal is to provide researchers with an informative and comprehensive view of EEG data to support their investigations.

	\section{Data Acquisition}
	\par To demonstrate the proposed visualization technique, EEG data will be acquired from an existing dataset. The chosen dataset is the "Open access database of EEG signals recorded during imagined speech" \cite{10.1117/12.2255697}. This dataset contains EEG recordings during the imagined pronunciation of vowels and commands, as well as EEG and audio recordings during the actual pronunciation. The dataset includes recordings from 15 Argentinian volunteers between the ages of 24 and 28, with an equal representation of males and females \cite{10.1117/12.2255697}. The data aims to enable accessibility to EEG records during imagined speech for future research on Brain-Computer Interfaces (BCI) that classify words based on their imagination. Although this dataset serves as the initial data source for the proposed visualization, future research intends to develop a custom EEG database in collaboration with local health institutions.

	\section{Database Structure}
	The EEG dataset is organized to facilitate data manipulation and analysis. Each row in the dataset corresponds to a subject, and the data is arranged as follows: EEG signals from different electrodes, modalities (imagined or pronounced), and stimulus codes representing different categories of stimuli (e.g., letters and commands). The modalities distinguish between imagined and pronounced speech, while the stimulus codes identify specific categories of stimuli. Figure \ref{fig:visu04} shows a sample of the initial rows in the database, and Figure \ref{fig:visu05} displays the last rows.

	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{../presentation/images/visu04}
		\caption{Sample of initial rows in the EEG database}
		\label{fig:visu04}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=.9\linewidth]{../presentation/images/visu05}
		\caption{Sample of last rows in the EEG database}
		\label{fig:visu05}
	\end{figure}

	\section{Pre-processing}
	To facilitate data manipulation and visualization, pre-processing techniques are applied to the EEG data. The data is grouped and organized to ensure seamless interactions and efficient representation. Figure \ref{fig:visu06} demonstrates the pre-processed and grouped data, ready for visualization.

	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{../presentation/images/visu06}
		\caption{Pre-processed and grouped EEG data}
		\label{fig:visu06}
	\end{figure}

	\section{Case Studies}
	The proposed visualization method will be evaluated through case studies using real EEG data. The case studies will focus on different subjects and stimuli to demonstrate the effectiveness and utility of the proposed visualization in various scenarios.

	\section{Visualization Inspired by EPviz \cite{currey2023epviz}}
	The proposed visualization method draws inspiration from EPviz, which effectively uses line graphs to visualize EEG data \cite{currey2023epviz}. EPviz visualizes EEG signals captured by all electrodes, providing a general overview of the data. However, the visualization lacks detailed views, which may limit the ability to discern specific patterns and features.

	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{../presentation/images/epviz00}
		\caption{EPviz - Line graph visualization}
		\label{fig:epviz00}
	\end{figure}

	\section{Visualization Inspired by \cite{9098189}}
	Another relevant methodology uses topological color maps to indicate signal energy at each sensor, offering insights into brain activity \cite{9098189}. The visualization in Figure \ref{fig:visu01} provides an informative representation of regions with intense brain activity during the corresponding time period. However, the interpolation of measured values may lead to potential misinterpretations of signal intensities according to gradients.

	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{../presentation/images/visu01}
		\caption{Topological visualization}
		\label{fig:visu01}
	\end{figure}

	\section{Visualization Inspired by \cite{8937083}}
	This methodology simplifies the visualization to display brain activity at four different moments \cite{8937083}. However, similar to the previous visualization, the gradient issue persists, potentially leading to incorrect interpretations.

	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{../presentation/images/visu02}
		\caption{Topological visualization}
		\label{fig:visu02}
	\end{figure}

	\section{Proposal}
	The proposed visualization method aims to overcome the limitations of existing techniques. It includes line graphs and energy visualizations combined with a non-gradient representation of electrode positions in the 10-20 system. The interactive features allow users to select subjects and stimuli, explore specific signal details, view the signal's origin, and amplify the displayed curves. Additionally, the visualization will include a bar showing the total energy of the displayed signal interval. The use of high-contrast colors will aid in perceptual differentiation. Figures \ref{fig:g3714} and \ref{fig:g3762} illustrate the general and specific views of the proposed visualization.

	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{../presentation/images/g3714}
		\caption{General view of the proposed visualization}
		\label{fig:g3714}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{../presentation/images/g3762}
		\caption{Specific view of the proposed visualization}
		\label{fig:g3762}
	\end{figure}

	\section{Future Work}
	As the research progresses, the proposed visualization will be further developed to display the hierarchical decomposition of captured waves into their respective components ($\alpha$, $\beta$, $\theta$, $\sigma$). Additionally, the visualization will show the categories and classes to which each signal belongs.

	\section{Code Repository}
	To access the source code, please visit: \href{https://github.com/ensismoebius/VisualizacaoDeInformacao}{https://github.com/ensismoebius/VisualizacaoDeInformacao}

	\section{Conclusion}
	This work proposes a novel visualization method for EEG data, incorporating line graphs and energy visualizations with a non-gradient representation of electrode positions in the 10-20 system. The proposed visualization aims to facilitate EEG data analysis and interpretation by offering interactive features for subject and stimulus selection, as well as specific signal exploration. High-contrast colors will be employed to enhance perceptual clarity. Future research will extend the proposed visualization to include hierarchical representations of signal components and their associated categories and classes.

	\begin{acks}
		The author would like to thank the Universidade Estadual Paulista Júlio de Mesquita Filho for its support and resources during this research.
	\end{acks}

	\section{References}
	\bibliographystyle{ACM-Reference-Format}
	\bibliography{../presentation/bibliography.bib}

\end{document}

### 2023-07-16 article/article.tex
Almost there!

@@
-\documentclass[format=acmtog]{acmart}
+\documentclass[format=sigconf]{acmart}
 
-\title{Visualizing EEG signals}
+\title{Enhancing the EEG signals visualization}
 
@@
 The dataset includes recordings from 15 Argentinian volunteers between the ages of 24 and 28, with an equal representation of males and females \cite{10.1117/12.2255697}.
-The data aims to enable accessibility to EEG records during imagined speech for future research on Brain-Computer Interfaces (BCI) that classify words based on their imagination.
-Although this dataset serves as the initial data source for the proposed visualization, future research intends to develop a custom EEG database in collaboration with local health institutions.
+Although this dataset serves as the initial data source for the proposed visualization, our future research intends to develop a custom EEG database in collaboration with local health institutions.
 
 	\section{Database Structure}
-	The EEG dataset is organized to facilitate data manipulation and analysis.
-Each row in the dataset corresponds to a subject, and the data is arranged as follows: EEG signals from different electrodes, modalities (imagined or pronounced), and stimulus codes representing different categories of stimuli (e.g., letters and commands).
+		\par Each row in the dataset corresponds to a subject-stimuli-modality set, and the data is arranged as follows: EEG signals from different electrodes, modalities (imagined or pronounced), and stimulus codes representing different categories of stimuli (e.g., letters and commands).
 The modalities distinguish between imagined and pronounced speech, while the stimulus codes identify specific categories of stimuli.
@@
 
-	\begin{figure}
+		\begin{figure}[h]
 			\centering
@@
 	\section{Pre-processing}
-	To facilitate data manipulation and visualization, pre-processing techniques are applied to the EEG data.
+		\par To facilitate data manipulation and visualization, pre-processing techniques are applied to the EEG data.
 The data is grouped and organized to ensure seamless interactions and efficient representation.
@@
 
-	\begin{figure}
+		\begin{figure}[h]
 			\centering
 			\includegraphics[width=\linewidth]{../presentation/images/visu06}
-		\caption{Pre-processed and grouped EEG data}
+			\caption{Pre-processed and Grouped EEG Data: Note the columns named after its respective source (i.e., the sensors) and the last three ones "modalidade," "Estímulo," and "Artefatos," which are, respectively, the modality, stimuli and artifacts.}
 			\label{fig:visu06}
@@
 	\section{Case Studies}
-	The proposed visualization method will be evaluated through case studies using real EEG data.
+		\par The proposed visualization method will be evaluated through case studies using real EEG data.
 The case studies will focus on different subjects and stimuli to demonstrate the effectiveness and utility of the proposed visualization in various scenarios.
 
-	\section{Visualization Inspired by EPviz \cite{currey2023epviz}}
-	The proposed visualization method draws inspiration from EPviz, which effectively uses line graphs to visualize EEG data \cite{currey2023epviz}.
+		\subsection{Visualization Inspired by EPviz \cite{currey2023epviz}}
+			\par The proposed visualization method draws inspiration from EPviz, which effectively uses line graphs to visualize EEG data \cite{currey2023epviz}.
 EPviz visualizes EEG signals captured by all electrodes, providing a general overview of the data.
@@
 
-	\begin{figure}
+			\begin{figure}[h]
 				\centering
@@
 
-	\section{Visualization Inspired by \cite{9098189}}
-	Another relevant methodology uses topological color maps to indicate signal energy at each sensor, offering insights into brain activity \cite{9098189}.
+		\subsection{Visualization Inspired by \cite{9098189}}
+			\par Another relevant methodology uses topological color maps to indicate signal energy at each sensor, offering insights into brain activity \cite{9098189}.
 The visualization in Figure \ref{fig:visu01} provides an informative representation of regions with intense brain activity during the corresponding time period.
@@
 
-	\section{Visualization Inspired by \cite{8937083}}
-	This methodology simplifies the visualization to display brain activity at four different moments \cite{8937083}.
+		\subsection{Visualization Inspired by \cite{8937083}}
+			\par This methodology shown in Figure \ref{fig:visu02} simplifies the visualization to display brain activity at four different moments \cite{8937083}.
 However, similar to the previous visualization, the gradient issue persists, potentially leading to incorrect interpretations.
 
-	\begin{figure}
+			\begin{figure}[h]
 				\centering
 				\includegraphics[width=\linewidth]{../presentation/images/visu02}
-		\caption{Topological visualization}
+				\caption{Topological visualization over time}
 				\label{fig:visu02}
@@
 	\section{Proposal}
-	The proposed visualization method aims to overcome the limitations of existing techniques.
+		\par The proposed visualization method aims to overcome the limitations of existing techniques.
 It includes line graphs and energy visualizations combined with a non-gradient representation of electrode positions in the 10-20 system.
@@
 
-	\begin{figure}
+		\begin{figure}[h]
 			\centering
 			\includegraphics[width=\linewidth]{../presentation/images/g3714}
-		\caption{General view of the proposed visualization}
+			\caption{Specific view of the proposed visualization}
 			\label{fig:g3714}
@@
 
-	\begin{figure}
+		\begin{figure}[h]
 			\centering
 			\includegraphics[width=\linewidth]{../presentation/images/g3762}
-		\caption{Specific view of the proposed visualization}
+			\caption{General view of the proposed visualization}
 			\label{fig:g3762}
@@
 
+	\section{Implementation}
+		\par The visualization was implemented using the Python3 \cite{Python3} programming language due to its extensive range of data visualization and manipulation libraries.
+It is important to note that the final result differs slightly from the proposal, however, this does not compromise the quality of the final product, as can be seen in Figure \ref{fig:screenshot01} and \ref{fig:screenshot02}.
+
+		\begin{figure}[h]
+			\centering
+			\includegraphics[width=\linewidth]{images/screenshot01}
+			\caption{The application screenshot in specific mode: All signals are represented separately.}
+			\label{fig:screenshot01}
+		\end{figure}
+
+		\begin{figure}[h]
+			\centering
+			\includegraphics[width=\linewidth]{images/screenshot02}
+			\caption{The application screenshot in general mode: All signals are represented in a single plot.}
+			\label{fig:screenshot02}
+		\end{figure}
+
+		\subsection{User interface discussion}
+			\par Focusing on the left side of the visualization: Like is shown in Figure \ref{fig:screenshotleft}, the sensors that are being used are represented by circles with vivid and contrasting colors which matches with its respectively plot on the right side, while the unused sensors are represented only by their names.
+At the top of each circle, there is a bar representing the corresponding signal's energy captured by that sensor.
+It is noteworthy that each signal may have different energy levels.
+
+			\begin{figure}[h]
+				\centering
+				\includegraphics[width=\linewidth]{images/screenshotLeft}
+				\caption{The sensors and its captured energy are represented by the colored circles and their top bars respectively.}
+				\label{fig:screenshotleft}
+			\end{figure}
+
+			\par The top section shown in Figure \ref{fig:screenshottop} is where the data filters reside: The first one "Selecione a modalidade" is a selector of the modality of the speech: Imagined or pronounced.
+Just setting this value alone does not affect the visualization because it needs the type of stimuli too.
+At the "Selecione o estímulo" selector is possible to set the type of stimuli which the visualization are needed.
+Considering that the previous selector is already set, this will trigger the change on the left and right parts of the screen showing the data visualization for the first subject.
+The subject can be changed using the "Selecione o sujeito" selector.
+Finally, the "Selecione o artefato" selector filters if data with artifacts are shown or not shown.
+
+			\begin{figure}[h]
+				\centering
+				\includegraphics[width=\linewidth]{images/screenshotTop}
+				\caption{The four selectors of the visualization: "Selecione a modalidade", "Selecione o estímulo", "Selecione o artefato" and "Selecione o sujeito"}
+				\label{fig:screenshottop}
+			\end{figure}
+
+			\par The right section (Figure \ref{fig:screenshotright}) displays the plots of the signals captured by the sensors.
+Each plot has a color matching to its respective sensor, and to avoid misinterpretations, there are labels on the right.
+This section changes when new filters are set and when the switch "Visão geral" depicted in Figure \ref{fig:screenshotbotton} is changed.
+Here, it is possible to zoom in on data, hide plots by clicking on labels, and even save the results to a file.
+
+			\begin{figure}[h]
+				\centering
+				\includegraphics[width=\linewidth]{images/screenshotRight}
+				\caption{The right section of the visualization: The signals may be shown separately or in a single plot.}
+				\label{fig:screenshotright}
+			\end{figure}
+
+			\begin{figure}[h]
+				\centering
+				\includegraphics{images/screenshotBotton}
+				\caption{This button switches between "General" and "Specific" modes.}
+				\label{fig:screenshotbotton}
+			\end{figure}
+		\subsection{Source code}
+
+			\par The code is designed to load EEG data from a MATLAB file, preprocess it.
+This visualization uses Panel, Plotly, SciPy, Pandas, BeautifulSoup and NumPy pyhton libraries.
+The code consists of two main classes: \texttt{Dashdata} and \texttt{Dashboard}.
+
+			\par The \texttt{Dashdata} class is responsible for loading and processing EEG data. The main tasks of this class are as follows:
+
+			\begin{itemize}
+
+				\item{\textbf{loading EEG Data}}: The \texttt{Dashdata} class loads EEG data from a MATLAB file using the \texttt{scipy.io.loadmat} function.
+The EEG data is stored in a MATLAB struct format, and the class uses \texttt{squeeze\_me} and \texttt{mat\_dtype} options to convert the data into a more usable format.
+
+				\item{\textbf{data preprocessing}}: After loading the data, the class creates a Pandas DataFrame called \texttt{dataframe} to store the EEG data.
+The EEG signals for specific sensors are combined into arrays, and the DataFrame is updated accordingly.
+This step simplifies data handling and allows easier access to EEG signal data for visualization.
+
+				\item{\textbf{setting up Properties}}: The class sets up properties to store essential information, such as the relationship between EEG sensors and their corresponding colors.
+This mapping is useful for visualizing EEG signals with different colors representing different sensors.
+
+				\item{\textbf{mapping Modalities, Stimuli, and Artifacts}}: The \texttt{Dashdata} class provides dictionaries to map descriptive names of modalities, stimuli, and artifacts to their respective numeric codes.
+This mapping facilitates user interaction, as select widgets can be populated with descriptive options.
+
+				\item{\textbf{loading brain Visualization}}: The class loads an SVG image of the brain, which can be used for visualizing the locations of EEG sensors on the brain.
+This SVG image is used in the dashboard to enhance the user experience and provide context to the EEG data.
+			\end{itemize}
+
+			\par The \texttt{Dashboard} class is designed to create an interactive EEG Data Visualization Dashboard using Panel and Plotly libraries.
+It utilizes the \texttt{Dashdata} class to access preprocessed EEG and visual elements data.
+
+			\begin{itemize}
+				\item{\textbf{widgets and UI Layout}} The dashboard creates various widgets for user interaction, such as selects for modalities, stimuli, artifacts, and subjects.
+Additionally, a switch widget is used to toggle between general and detailed views of the EEG data.
+The dashboard's layout is arranged using rows and columns to organize the visual elements effectively.
+
+				\item{\textbf{event handling}} The class defines callback methods to handle user interactions with the widgets.
+These methods update the visualization based on the user's selections for modalities, stimuli, artifacts, subjects, and the general view toggle.
+The EEG data is filtered and plotted accordingly to provide an interactive and dynamic visualization experience.
+
+				\item{\textbf{data visualization}} The dashboard uses Plotly to visualize the EEG data.
+It creates line plots representing EEG signals for different sensors.
+Depending on the user's selection, the dashboard can display single-panel or multiple-panel plots.
+The latter provides a more detailed view of the EEG signals.
+			\end{itemize}
+
 	\section{Future Work}
-	As the research progresses, the proposed visualization will be further developed to display the hierarchical decomposition of captured waves into their respective components ($\alpha$, $\beta$, $\theta$, $\sigma$).
+		\par As the research progresses, the proposed visualization will be further developed to display the hierarchical decomposition of captured waves into their respective components ($\alpha$, $\beta$, $\theta$, $\sigma$).
 Additionally, the visualization will show the categories and classes to which each signal belongs.
@@
 	\section{Code Repository}
-	To access the source code, please visit: \href{https://github.com/ensismoebius/VisualizacaoDeInformacao}{https://github.com/ensismoebius/VisualizacaoDeInformacao}
+	\par To access the source code, please visit:\newline \href{https://github.com/ensismoebius/VisualizacaoDeInformacao}{\textbf{https://github.com/ensismoebius/VisualizacaoDeInformacao}}
 
 	\section{Conclusion}
-	This work proposes a novel visualization method for EEG data, incorporating line graphs and energy visualizations with a non-gradient representation of electrode positions in the 10-20 system.
+		\par This work proposes a novel visualization method for EEG data, incorporating line graphs and energy visualizations with a non-gradient representation of electrode positions in the 10-20 system.
 The proposed visualization aims to facilitate EEG data analysis and interpretation by offering interactive features for subject and stimulus selection, as well as specific signal exploration.

### 2023-07-17 article/article.tex
For (if any) god's sake! Almost there! Just lacks the explanation of the sourcecode!

@@
 \documentclass[format=sigconf]{acmart}
+
+\input{preamble.tex}
 
@@
 		\par Electroencephalogram (EEG) data is widely used in neuroscience research to study brain activity.
-EEG records electrical signals generated by brain neurons and reflects cognitive processes, making it a valuable tool in various applications, including Brain-Computer Interfaces (BCI) and clinical diagnosis of neurological disorders \cite{8937083}.
+EEG records electrical signals generated by brain neurons during a task making it a valuable tool in various applications, including Brain-Computer Interfaces (BCI) and clinical diagnosis of neurological states \cite{8937083}.
 Analyzing EEG data, however, poses challenges due to its complexity, such as a vast number of emitting sources (neurons) and potential electromagnetic interferences from external sources like cell phones, electric motors, and magnetic fields from wires \cite{8937083}.
-To facilitate EEG data interpretation and visualization, it is crucial to develop effective and efficient visualization techniques that allow researchers to gain valuable insights from the data.
-This paper proposes a novel visualization method for EEG data, combining line graphs and energy visualizations with a display of the electrode positions in the 10-20 system \cite{sistema10-20}.
-The proposed visualization will be interactive, allowing users to select subjects and stimuli and explore specific signal details.
+To facilitate EEG data interpretation and visualization, it is crucial to develop effective and efficient techniques that allow researchers to gain valuable insights from the data.
+This paper proposes a visualization method for EEG data, combining line graphs and energy visualizations with a display of the electrode positions in the 10-20 system \cite{sistema10-20}.
+The proposed visualization will be interactive, allowing users to select subjects and stimuli and explore signal details.
 The goal is to provide researchers with an informative and comprehensive view of EEG data to support their investigations.
@@
 	\section{Data Acquisition}
-		\par To demonstrate the proposed visualization technique, EEG data will be acquired from an existing dataset.
+
+		\par To demonstrate the proposed visualization technique, EEG data was acquired from an existing dataset.
 The chosen dataset is the "Open access database of EEG signals recorded during imagined speech" \cite{10.1117/12.2255697}.
 This dataset contains EEG recordings during the imagined pronunciation of vowels and commands, as well as EEG and audio recordings during the actual pronunciation.
-The dataset includes recordings from 15 Argentinian volunteers between the ages of 24 and 28, with an equal representation of males and females \cite{10.1117/12.2255697}.
-Although this dataset serves as the initial data source for the proposed visualization, our future research intends to develop a custom EEG database in collaboration with local health institutions.
+The dataset includes recordings from 15 Argentinian volunteers between the ages of 24 and 28, with an equal representation of males and females \cite{10.1117/12.2255697}.\newline
+
+		\par As shown in Figure \ref{fig:sistema10-20}, the data was acquired using the 10-20 system \cite{sistema10-20} which consist of electrodes spaced by 20\% of the head size and a margin of 10\% in relation to \textit{nasion}, \textit{inion} and to the preauricular point.
+In this specific database only the sensors $F3$, $F4$, $C3$, $C4$, $P3$ and $P4$ was used.
+
+		\begin{figure}[h]
+			\centering
+			\includegraphics[width=\linewidth]{../presentation/images/sistema10-20}
+			\caption{system 10-20: The electrodes are evenly separated across the scalp of the subject. The A1 sensor is the preauricular point. Source: \cite{sistema10-20}}
+			\label{fig:sistema10-20}
+		\end{figure}
+
+		\par Although this dataset serves as the initial data source for the proposed visualization, our future research intends to develop a custom EEG database in collaboration with local health institutions.
 
@@
 The modalities distinguish between imagined and pronounced speech, while the stimulus codes identify specific categories of stimuli.
-Figure \ref{fig:visu04} shows a sample of the initial rows in the database, and Figure \ref{fig:visu05} displays the last rows.
+Figure \ref{fig:visu04} shows a sample of the initial rows in the database, and Figure \ref{fig:visu05} displays the last rows.\newline
+
+		\par Each line consist in a series of numbers organized as follows:
+		\begin{itemize}
+			\item F3 - 0:4095
+			\item F4 - 4096:8191
+			\item C3 - 8192:12287
+			\item C4 - 12288:16383
+			\item P3 - 16384:20479
+			\item P4 - 20480:24575
+			\item modality - 24576:24576
+			\item estimuli - 24577:24577
+			\item artifact - 24578:24578
+		\end{itemize}
+
+		\par Modality can be 1 for imagined speech or 2 for pronounced speech.
+Stimuli assumes 1: A, 2: E, 3: I, 4:O and 5:U and 6:\textit{Arriba}, 7: \textit{Abajo}, 8: \textit{Adelante}, 9: \textit{Atrás}, 10: \textit{Derecha}, 11: \textit{Izquierda}.
 
@@
 
-	\section{Pre-processing}
+	\section{Preprocessing}
 		\par To facilitate data manipulation and visualization, pre-processing techniques are applied to the EEG data.
-The data is grouped and organized to ensure seamless interactions and efficient representation.
+The data is grouped and organized to ensure better interactions and efficient representation.
 Figure \ref{fig:visu06} demonstrates the pre-processed and grouped data, ready for visualization.
@@
 	\section{Case Studies}
-		\par The proposed visualization method will be evaluated through case studies using real EEG data.
-The case studies will focus on different subjects and stimuli to demonstrate the effectiveness and utility of the proposed visualization in various scenarios.
+		\par The proposed visualization method drew inspiration from case studies that utilized real EEG data.
+These case studies focused on various subjects and stimuli, showcasing their effectiveness and utility.
+Accordingly, certain features will be incorporated, while others will be discarded.
 
-		\subsection{Visualization Inspired by EPviz \cite{currey2023epviz}}
-			\par The proposed visualization method draws inspiration from EPviz, which effectively uses line graphs to visualize EEG data \cite{currey2023epviz}.
-EPviz visualizes EEG signals captured by all electrodes, providing a general overview of the data.
-However, the visualization lacks detailed views, which may limit the ability to discern specific patterns and features.
+		\subsection{Visualization Inspired by \cite{currey2023epviz}}
+			\par EPviz uses line graphs to visualize EEG data \cite{currey2023epviz} and provide a general overview of the data.
+The visualization by lines is efficient because it shows the high and low frequency components.
+In the example shown in Figure \ref{fig:epviz00}, the EPViz program visualizes the signals captured by all the electrodes, providing a good overview.
+However, it lacks the detailed view that would allow a more accurate analysis of the displayed curves.
 
@@
 		\subsection{Visualization Inspired by \cite{9098189}}
-			\par Another relevant methodology uses topological color maps to indicate signal energy at each sensor, offering insights into brain activity \cite{9098189}.
-The visualization in Figure \ref{fig:visu01} provides an informative representation of regions with intense brain activity during the corresponding time period.
-However, the interpolation of measured values may lead to potential misinterpretations of signal intensities according to gradients.
+			\par Another relevant methodology uses topological color maps to indicate signal energy at each sensor.
+This visualization approach shown in Figure \ref{fig:visu01} provides an informative representation of regions with intense brain activity during the corresponding time period.
+However, the view makes a interpolation of measured values leading to potential misinterpretations of signal intensities according to gradients.
 
@@
 		\subsection{Visualization Inspired by \cite{8937083}}
-			\par This methodology shown in Figure \ref{fig:visu02} simplifies the visualization to display brain activity at four different moments \cite{8937083}.
+			\par The methodology shown in Figure \ref{fig:visu02} simplifies the visualization to display brain activity at four different moments.
 However, similar to the previous visualization, the gradient issue persists, potentially leading to incorrect interpretations.
@@
 	\section{Proposal}
-		\par The proposed visualization method aims to overcome the limitations of existing techniques.
-It includes line graphs and energy visualizations combined with a non-gradient representation of electrode positions in the 10-20 system.
-The interactive features allow users to select subjects and stimuli, explore specific signal details, view the signal's origin, and amplify the displayed curves.
-Additionally, the visualization will include a bar showing the total energy of the displayed signal interval.
+		\par The proposed visualization method includes line graphs and energy visualizations combined with a non-gradient representation of electrode positions in the 10-20 system.
+The interactive features allow users to select subjects and stimuli, explore specific signal details, view the signal's origin, and scale up or down the displayed curves.
+Additionally, the visualization will include bars showing the total energy of the displayed signal interval.
 The use of high-contrast colors will aid in perceptual differentiation.
-Figures \ref{fig:g3714} and \ref{fig:g3762} illustrate the general and specific views of the proposed visualization.
+Figures \ref{fig:g3714} and \ref{fig:g3762} illustrate the general and specific views proposed.
 
@@
 
+		\par Both the \textbf{subject and stimulus selection} and the checkbox are integral components of the \textbf{visualization cycle} \cite{munzner2014visualization}.
+When modifying the type of vision, stimuli and/or the analyzed subject, the view must promptly respond by updating the displayed data.\newline
+
+		\par The use of \textbf{high contrast} colors aids in easily locating the origin of the data \cite{spence2014information}, preventing the common problem of differentiating data when very similar colors are employed.\newline
+
+		\par The \textbf{magnification} feature enables a detailed view of each signal \cite{tufte1983visual}, facilitating the visualization of information linked to low and high-frequency signals.
+This provides the identification of \textbf{objects according to their "silhouette"} \cite{tufte2006beautiful}.\newline
+
+		\par It's worth noting that the attributes utilized in the proposal have a \textbf{sequential} \cite{kirk2012data} order for the amplitude and frequency of the signals over time (line graphs), while simultaneously being \textbf{categorical} \cite{kirk2012data} because the frequency analysis can reveal valuable insights about the subject being analyzed.\newline
+
+		\par The energy attribute (vertical bar on the side of the line graph) is \textbf{quantitative}.\newline
+
+		\par Regarding \textbf{categorical} attributes, the region to the left of the graphs also deserves attention.
+This section indicates which brain regions are emitting specific signals, allowing, for example, the inference of the most active brain regions during thought execution and/or action.\newline
+
+		\par In terms of \textbf{semiotic categories} \cite{santaella2017semiotica} it is possible to highlight:
+		\begin{itemize}
+			\item firstness: Colors that stand out and immediately call the user's attention.
+			\item secondness: The action/reaction applied to controls and images.
+			\item thirdness: The consequent interpretation of the image presented as well as the reasoning necessary for understanding what is shown.
+		\end{itemize}
+
 	\section{Implementation}
-		\par The visualization was implemented using the Python3 \cite{Python3} programming language due to its extensive range of data visualization and manipulation libraries.
+		\par The visualization was implemented using the Python3 \cite{Python3} programming language due to its extensive set of data visualization and manipulation libraries.
 It is important to note that the final result differs slightly from the proposal, however, this does not compromise the quality of the final product, as can be seen in Figure \ref{fig:screenshot01} and \ref{fig:screenshot02}.
@@
 
+			\lstinputlisting[language=Python]{code/test.py}
+
 			\begin{itemize}
@@
 
-	\section{References}
 	\bibliographystyle{ACM-Reference-Format}

### 2023-07-18 article/article.tex
Finished!!!!

@@
 	\begin{abstract}
-		Electroencephalogram (EEG) data has inherent complexity, including a large volume, diverse frequencies (e.g., alpha, beta, theta, sigma), and numerous emitting sources (neurons).
+		Electroencephalogram (EEG) data has inherent complexity, including a large volume, diverse frequencies (e.g., $\alpha$, $\beta$, $\theta$, $\sigma$), and numerous emitting sources (neurons).
 Additionally, potential electromagnetic interferences from external sources pose challenges during EEG analysis.
@@
 		\par As shown in Figure \ref{fig:sistema10-20}, the data was acquired using the 10-20 system \cite{sistema10-20} which consist of electrodes spaced by 20\% of the head size and a margin of 10\% in relation to \textit{nasion}, \textit{inion} and to the preauricular point.
-In this specific database only the sensors $F3$, $F4$, $C3$, $C4$, $P3$ and $P4$ was used.
+In this specific database only the electrodes $F3$, $F4$, $C3$, $C4$, $P3$ and $P4$ was used.
 
@@
 			\centering
+			\caption{system 10-20: The electrodes are evenly separated across the scalp of the subject. The A1 electrode is the preauricular point. Source: \cite{sistema10-20}}
 			\includegraphics[width=\linewidth]{../presentation/images/sistema10-20}
-			\caption{system 10-20: The electrodes are evenly separated across the scalp of the subject. The A1 sensor is the preauricular point. Source: \cite{sistema10-20}}
 			\label{fig:sistema10-20}
@@
 
-		\par Each line consist in a series of numbers organized as follows:
+		\par Being F3, F4, C3, C4, P3 and P4 the name of the electrodes in the 10-20 system, each line consist in a series of numbers organized as follows:
+
 		\begin{itemize}
@@
 		\par Modality can be 1 for imagined speech or 2 for pronounced speech.
-Stimuli assumes 1: A, 2: E, 3: I, 4:O and 5:U and 6:\textit{Arriba}, 7: \textit{Abajo}, 8: \textit{Adelante}, 9: \textit{Atrás}, 10: \textit{Derecha}, 11: \textit{Izquierda}.
+Stimuli assumes 1: A, 2: E, 3: I, 4:O and 5:U and 6:\textit{Arriba}, 7: \textit{Abajo}, 8: \textit{Adelante}, 9: \textit{Atrás}, 10: \textit{Derecha}, 11: \textit{Izquierda} finally artifact assumes 1 for no eye blinking and 2 otherwise.
 
@@
 			\centering
+			\caption{Sample of initial rows in the EEG database}
 			\includegraphics[width=\linewidth]{../presentation/images/visu04}
-			\caption{Sample of initial rows in the EEG database}
 			\label{fig:visu04}
@@
 			\centering
+			\caption{Sample of last rows in the EEG database}
 			\includegraphics[width=.9\linewidth]{../presentation/images/visu05}
-			\caption{Sample of last rows in the EEG database}
 			\label{fig:visu05}
@@
 			\centering
+			\caption{Pre-processed and Grouped EEG Data: Note the columns named after its respective source (i.e., the electrodes) and the last three ones "modalidade," "Estímulo," and "Artefatos," which are, respectively, the modality, stimuli and artifacts.}
 			\includegraphics[width=\linewidth]{../presentation/images/visu06}
-			\caption{Pre-processed and Grouped EEG Data: Note the columns named after its respective source (i.e., the sensors) and the last three ones "modalidade," "Estímulo," and "Artefatos," which are, respectively, the modality, stimuli and artifacts.}
 			\label{fig:visu06}
@@
 				\centering
+				\caption{EPviz - Line graph visualization}
 				\includegraphics[width=\linewidth]{../presentation/images/epviz00}
-				\caption{EPviz - Line graph visualization}
 				\label{fig:epviz00}
@@
 		\subsection{Visualization Inspired by \cite{9098189}}
-			\par Another relevant methodology uses topological color maps to indicate signal energy at each sensor.
+			\par Another relevant methodology uses topological color maps to indicate signal energy at each electrode.
 This visualization approach shown in Figure \ref{fig:visu01} provides an informative representation of regions with intense brain activity during the corresponding time period.
@@
 				\centering
+				\caption{Topological visualization}
 				\includegraphics[width=\linewidth]{../presentation/images/visu01}
-				\caption{Topological visualization}
 				\label{fig:visu01}
@@
 				\centering
+				\caption{Topological visualization over time}
 				\includegraphics[width=\linewidth]{../presentation/images/visu02}
-				\caption{Topological visualization over time}
 				\label{fig:visu02}
@@
 			\centering
+			\caption{Specific view of the proposed visualization}
 			\includegraphics[width=\linewidth]{../presentation/images/g3714}
-			\caption{Specific view of the proposed visualization}
 			\label{fig:g3714}
@@
 			\centering
+			\caption{General view of the proposed visualization}
 			\includegraphics[width=\linewidth]{../presentation/images/g3762}
-			\caption{General view of the proposed visualization}
 			\label{fig:g3762}
@@
 			\centering
+			\caption{The application screenshot in specific mode: All signals are represented separately.}
 			\includegraphics[width=\linewidth]{images/screenshot01}
-			\caption{The application screenshot in specific mode: All signals are represented separately.}
 			\label{fig:screenshot01}
@@
 			\centering
+			\caption{The application screenshot in general mode: All signals are represented in a single plot.}
 			\includegraphics[width=\linewidth]{images/screenshot02}
-			\caption{The application screenshot in general mode: All signals are represented in a single plot.}
 			\label{fig:screenshot02}
@@
 		\subsection{User interface discussion}
-			\par Focusing on the left side of the visualization: Like is shown in Figure \ref{fig:screenshotleft}, the sensors that are being used are represented by circles with vivid and contrasting colors which matches with its respectively plot on the right side, while the unused sensors are represented only by their names.
-At the top of each circle, there is a bar representing the corresponding signal's energy captured by that sensor.
+			\par Focusing on the left side of the visualization: Like is shown in Figure \ref{fig:screenshotleft}, the electrodes that are being used are represented by circles with vivid and contrasting colors which matches with its respectively plot on the right side, while the unused electrodes are represented only by their names.
+At the top of each circle, there is a bar representing the corresponding signal's energy captured by that electrode.
 It is noteworthy that each signal may have different energy levels.
@@
 				\centering
+				\caption{The electrodes and its captured energy are represented by the colored circles and their top bars respectively.}
 				\includegraphics[width=\linewidth]{images/screenshotLeft}
-				\caption{The sensors and its captured energy are represented by the colored circles and their top bars respectively.}
 				\label{fig:screenshotleft}
@@
 				\centering
+				\caption{The four selectors of the visualization: "Selecione a modalidade", "Selecione o estímulo", "Selecione o artefato" and "Selecione o sujeito"}
 				\includegraphics[width=\linewidth]{images/screenshotTop}
-				\caption{The four selectors of the visualization: "Selecione a modalidade", "Selecione o estímulo", "Selecione o artefato" and "Selecione o sujeito"}
 				\label{fig:screenshottop}
@@
 
-			\par The right section (Figure \ref{fig:screenshotright}) displays the plots of the signals captured by the sensors.
-Each plot has a color matching to its respective sensor, and to avoid misinterpretations, there are labels on the right.
+			\par The right section (Figure \ref{fig:screenshotright}) displays the plots of the signals captured by the electrodes.
+Each plot has a color matching to its respective electrode, and to avoid misinterpretations, there are labels on the right.
 This section changes when new filters are set and when the switch "Visão geral" depicted in Figure \ref{fig:screenshotbotton} is changed.
@@
 				\centering
+				\caption{The right section of the visualization: The signals may be shown separately or in a single plot.}
 				\includegraphics[width=\linewidth]{images/screenshotRight}
-				\caption{The right section of the visualization: The signals may be shown separately or in a single plot.}
 				\label{fig:screenshotright}
@@
 				\centering
+				\caption{This button switches between "General" and "Specific" modes.}
 				\includegraphics{images/screenshotBotton}
-				\caption{This button switches between "General" and "Specific" modes.}
 				\label{fig:screenshotbotton}
@@
 
-			\par The code is designed to load EEG data from a MATLAB file, preprocess it.
-This visualization uses Panel, Plotly, SciPy, Pandas, BeautifulSoup and NumPy pyhton libraries.
-The code consists of two main classes: \texttt{Dashdata} and \texttt{Dashboard}.
+			\par This section provides an overview of the most important code excerpts.
+The full code is available in the repository listed at the end of this document.
+This visualization utilizes the following Python libraries: Panel, Plotly, SciPy, Pandas, BeautifulSoup, and NumPy.
+It comprises two main classes: \texttt{Dashdata} and \texttt{Dashboard}.\newline
 
 			\par The \texttt{Dashdata} class is responsible for loading and processing EEG data. The main tasks of this class are as follows:
-
-			\lstinputlisting[language=Python]{code/test.py}
 
@@
 
+				\lstinputlisting[language=Python, caption={Loading a Matlab file}]{code/loadEEGData.py}
+
 				\item{\textbf{data preprocessing}}: After loading the data, the class creates a Pandas DataFrame called \texttt{dataframe} to store the EEG data.
-The EEG signals for specific sensors are combined into arrays, and the DataFrame is updated accordingly.
+The EEG signals for specific electrodes are combined into arrays, and the DataFrame is updated accordingly.
 This step simplifies data handling and allows easier access to EEG signal data for visualization.
+This is done using the \textit{\_joinIntoArray} function.
 
-				\item{\textbf{setting up Properties}}: The class sets up properties to store essential information, such as the relationship between EEG sensors and their corresponding colors.
-This mapping is useful for visualizing EEG signals with different colors representing different sensors.
+				\lstinputlisting[language=Python, caption={This function groups the columns}]{code/dataProcessingFunc.py}
+
+				\lstinputlisting[language=Python, caption={Grouping the columns}]{code/dataProcessing.py}
+
+				\item{\textbf{setting up Properties}}: The class sets up properties to store essential information, such as the relationship between EEG electrodes and their corresponding colors.
+This mapping is useful for visualizing EEG signals with different colors representing different electrodes.
+
+				\lstinputlisting[language=Python, caption={Color and sensor data}]{code/sensorData.py}
 
@@
 
-				\item{\textbf{loading brain Visualization}}: The class loads an SVG image of the brain, which can be used for visualizing the locations of EEG sensors on the brain.
-This SVG image is used in the dashboard to enhance the user experience and provide context to the EEG data.
+				\lstinputlisting[language=Python, caption={Dictionaries for widgets}]{code/widgetsDict.py}
+
+				\item{\textbf{loading brain Visualization}}: The class loads an SVG image of the brain, which serves the purpose of visualizing the locations of EEG electrodes on the brain.
+Incorporating this SVG image into the dashboard enhances the user experience and offers context to the EEG data.
+An additional advantage of this approach is that, due to the handcrafted nature of this resource, it can be readily replaced by another SVG image to meet new requirements and demands!
+
+				\lstinputlisting[language=Python, caption={Loading SVG image}]{code/loadSVG.py}
 			\end{itemize}
@@
 			\begin{itemize}
+				\item As aforementioned the SVG image is used to represent the brain.
+But this representation means nothing if it cannot be modified to reflect the visualization parameters.
+To do this two functions are used to update this image.
+
+				\lstinputlisting[language=Python, caption={Functions that updates the SVG image}]{code/SVGFunc.py}
+
 				\item{\textbf{widgets and UI Layout}} The dashboard creates various widgets for user interaction, such as selects for modalities, stimuli, artifacts, and subjects.
@@
 
-				\item{\textbf{event handling}} The class defines callback methods to handle user interactions with the widgets.
+				\item{\textbf{event handling}} This class defines callback methods to handle user interactions with the widgets.
 These methods update the visualization based on the user's selections for modalities, stimuli, artifacts, subjects, and the general view toggle.
@@
 				\item{\textbf{data visualization}} The dashboard uses Plotly to visualize the EEG data.
-It creates line plots representing EEG signals for different sensors.
+It creates line plots representing EEG signals for different electrodes.
 Depending on the user's selection, the dashboard can display single-panel or multiple-panel plots.
@@
 
-	\section{Future Work}
-		\par As the research progresses, the proposed visualization will be further developed to display the hierarchical decomposition of captured waves into their respective components ($\alpha$, $\beta$, $\theta$, $\sigma$).
-Additionally, the visualization will show the categories and classes to which each signal belongs.
+	\section{Conclusion and future work}
+		\par The non-gradient method of displaying data in conjunction with the capacity of data isolation offers more clarity and reduce misinterpretation of the data.
+But, despite the current state of this visualization being well-rounded, some features may be implemented: the capacity to dynamically load data in other formats, the decomposition of data into its sub-frequencies ($\alpha$, $\beta$, $\theta$, $\sigma$), and a real-time display of EEG.
+As research progresses, the proposed visualization will be further developed to incorporate these features.
 
@@
 		\par To access the source code, please visit:\newline \href{https://github.com/ensismoebius/VisualizacaoDeInformacao}{\textbf{https://github.com/ensismoebius/VisualizacaoDeInformacao}}
-
-	\section{Conclusion}
-		\par This work proposes a novel visualization method for EEG data, incorporating line graphs and energy visualizations with a non-gradient representation of electrode positions in the 10-20 system.
-The proposed visualization aims to facilitate EEG data analysis and interpretation by offering interactive features for subject and stimulus selection, as well as specific signal exploration.
-High-contrast colors will be employed to enhance perceptual clarity.
-Future research will extend the proposed visualization to include hierarchical representations of signal components and their associated categories and classes.
 

### 2023-07-18 article/code/SVGFunc.py.tex
Finished!!!!

# Function that changes the energy bar height
# "soup" is the SVG data
# "element_id" is the id of the energy bar that will be resized
# "new_height" is the new height of the energy bar
def _changeElementHeight(self, soup, element_id, new_height):

 # Find the element
 element = soup.find(id=element_id)

 # If it exists updates its height and paint it of 
 # black because initially the bars are transparent
 if element is not None:
   element['height'] = str(new_height/1000)
   element["style"] = 'fill:#000000'

# Function that paint the electrodes in the SVG image
# "soup" is the SVG data
# "sensorsTags" is the tag of the electrode to be painted
def _paintSensor(self, soup, sensorsTags):

 # Find the element
 element = soup.find(id=sensorsTags)

 # If it exists updates its color
 if element is not None:
   color = self.ddata.sensorToColorRelationship[sensorsTags]
   element["style"] = f'fill:{color}'

### 2023-07-18 article/code/dataProcessing.py.tex
Finished!!!!

# Loads the EEG section into a dataframe
self.dataframe = pd.DataFrame(mat['EEG'])

# Joins the columns into its respectives electrodes
self._joinIntoArray(0, 4096, 'F3', self.dataframe)
self._joinIntoArray(0, 4096, 'F4', self.dataframe)
self._joinIntoArray(0, 4096, 'C3', self.dataframe)
self._joinIntoArray(0, 4096, 'C4', self.dataframe)
self._joinIntoArray(0, 4096, 'P3', self.dataframe)
self._joinIntoArray(0, 4096, 'P4', self.dataframe)

# Joins the columns into its respectives classes
self._joinIntoValue(0,1,'Modality',self.dataframe)
self._joinIntoValue(0,1,'Estimuli',self.dataframe)
self._joinIntoValue(0,1,'Artifact',self.dataframe)

### 2023-07-19 dashboard/teste.py
Use and instalation instructions

@@ -1,63 +1,0 @@
-rom dash import Dash, html, dash_table, dcc, Input, Output
-import pandas as pd
-import plotly.express as px
-import plotly.graph_objs as go
-from plotly.subplots import make_subplots
-
-from scipy.io import loadmat
-import numpy as np
-
-from ipywidgets import interact, Dropdown, IntSlider
-from PIL import Image
-
-def joinIntoArray(start_col, end_col, newColumn, dataframe):
-    cols_to_join = dataframe.iloc[:, start_col:end_col].columns
-    dataframe[newColumn] = dataframe[cols_to_join].apply(lambda x: np.array(pd.to_numeric(x, errors='coerce')), axis=1)
-    dataframe.drop(cols_to_join, axis=1, inplace=True)
-
-def joinIntoValue(start_col, end_col, newColumn, dataframe):
-    cols_to_join = dataframe.iloc[:, start_col:end_col].columns
-    dataframe[newColumn] = dataframe[cols_to_join].apply(lambda x: pd.to_numeric(x, errors='coerce'), axis=1)
-    dataframe.drop(cols_to_join, axis=1, inplace=True)
-
-def loadData():
-    mat = loadmat(
-    '/home/ensismoebius/Documentos/UNESP/doutorado/databases/Base de Datos Habla Imaginada/S01/S01_EEG.mat',
-    struct_as_record=True, squeeze_me=True, mat_dtype=False
-    )
-
-    df = pd.DataFrame(mat['EEG'])
-
-    joinIntoArray(0, 4096, 'F3', df)
-    joinIntoArray(0, 4096, 'F4', df)
-    joinIntoArray(0, 4096, 'C3', df)
-    joinIntoArray(0, 4096, 'C4', df)
-    joinIntoArray(0, 4096, 'P3', df)
-    joinIntoArray(0, 4096, 'P4', df)
-    
-    joinIntoValue(0, 1, 'Modalidade', df)
-    joinIntoValue(0, 1, 'Estímulo', df)
-    joinIntoValue(0, 1, 'Artefatos', df)
-    
-    return mat
-
-def getEstimulos():
-        estimulos = {
-            1  : "A",
-            2  : "E",
-            3  : "I",
-            4  : "O",
-            5  : "U",
-            6  : "Arriba",
-            7  : "Abajo",
-            8  : "Adelante",
-            9  : "Atrás",
-            10 : "Derecha",
-            11 : "Izquierda",
-        }
-        
[…]
